---
title: "SickSeal_6018"
author: "T.Adachi, R.Holser"
date: "20211029"
output: 
  html_document:
    toc: true
---


<style type="text/css">
.main-container {
  max-width: 10000px;
  margin-left: auto;
  margin-right: auto;
}
</style>

options(encoding = "utf-8")


## MEMO
- This rmd file is made based on Kami_Matome.rmd for Adachi et al. 2021
  - Modified by R.Holser on 4-Aug-2022 for Holser et al. 2022


## Setting
```{r setting, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r timelog, echo = FALSE}
print(paste("updated at", Sys.time(), sep = " "))
```

## Libraries
```{r results = "asis", echo=FALSE,warning=FALSE, message = FALSE}
library(ggplot2)
library(tidyverse)
library(data.table)
library(patchwork)
library(ggthemes)
```

## Data loading
- Load dat_default.csv
  - daily summary
  - For now, this is made in Kami_Matome.rmd 
  - the original data is located at 
    - E:\\imtaiky\\Desktop\\Data\\20190129_KamiMatome\\OutputWv_from_IGOR

```{r data loading, results = "asis", echo=FALSE,warning=FALSE, message = FALSE}
#Daily data----
dat_default <- read.csv(file = paste(getwd(), "dat_default.csv", sep="/"))
#Mesopelagic => Pelagic for naming
dat_default$group <- str_replace_all(dat_default$group, pattern = "Mesopelagic", replacement = "Pelagic")
#6108 => 6018
dat_default$sealID <- gsub("ID_2017_PB_6108", "ID_2017_PB_6018", dat_default$sealID)

#save folder
dirToSave = paste(getwd(), "Results", sep="/")

#post-breeding seals
dat_PB <- filter(dat_default,
                 dat_default$PBorPM == "PB" &
                 dat_default$indID!=5 & ## ID_2011_PM_T35 
                 dat_default$indID!=55 & ## no data (9678))
                 dat_default$indID!=56 & ## no data (R415)
                 dat_default$indID!=66) ## strange data with minus values of bathy (4441)?@
#
dat_PB <- filter(dat_PB,
                 dat_PB$KamiNoSumPerDay != 0 &
                 dat_PB$ForDiveDurationSum != 0)
#group2
dat_PB$group2 = dat_PB$group
dat_PB$group2 <- gsub("Pelagic", "Control", dat_PB$group2)
dat_PB$group2 <- gsub("Benthic", "Control", dat_PB$group2)

#All Kami data points----
##read z-----
z <- fread(file="z.txt")
z$indID2 <- gsub("2017_PB_6108", "2017_PB_6018", z$indID2)
#add PB or PM
a <- grep("PB",z$indID2,value=F)
z$PBorPM[a] = 1
a <- grep("PM",z$indID2,value=F)
z$PBorPM[a] = 2
#add benthic/pelagic/sick
#meso
z$group <- rep("Pelagic",times=length(z$Day))
#bathy
a <- grep("X822",z$indID2,value=F)
z$group[a] = "Benthic"
a <- grep("X823",z$indID2,value=F)
z$group[a] = "Benthic"
a <- grep("5712",z$indID2,value=F)
z$group[a] = "Benthic"  
#sick
a <- grep("6018",z$indID2,value=F)
z$group[a] = "Sick"
#z_default
  z_default <- z
##read z2-----
z2 <- fread(file="z2.txt")
#add KamiNo to z_default
z_default$KamiNo <- z2$KamiNo
z2_default <- z_default  
#post-breeding seals
cond <- (z2_default$PBorPM == 1 & 
           z2_default$indID!=5 & 
           z2_default$indID!=55 & # no data (9678)
           z2_default$indID!=56 & # no data (R415)
           z2_default$indID!=66) # strange data with minus values of bathy (4441)
z2_PB <- z2_default[cond,]
#group2
z2_PB$group2 = z2_PB$group
z2_PB$group2 <- gsub("Pelagic", "Control", z2_PB$group2)
z2_PB$group2 <- gsub("Benthic", "Control", z2_PB$group2)

```


```{r}
Seals<-unique(dat_PB$sealID)
Kamis<-vector(mode="numeric",length=length(Seals))
MeanKamis<-vector(mode="numeric",length=length(Seals))

for (i in 1:length(Seals)){
  temp<-subset(dat_PB, sealID==Seals[i])
  Kamis[i]<-sum(temp$KamiNoSumPerDay)
  MeanKamis[i]<-mean(temp$KamiNoSumPerDay)
}

Kamis<-cbind(Seals,Kamis,MeanKamis)
```


## Paper Figures

```{r Kami/Day~Trip, echo=FALSE,warning=FALSE, message = FALSE}

gg1<-ggplot(data=subset(dat_PB, group!="Benthic"),aes(x=dayID, y=KamiNoSumPerDay))+
  geom_smooth(aes(fill=group, color=group), method="loess")+
  geom_hline(yintercept=1500, linetype="dashed")+
  geom_point(data=subset(dat_PB, group=="Sick"), aes(color=group), size=1.5)+
  scale_color_manual(values=c("royalblue","orange"), name="", labels=c("Normal", "Seal 6018"))+
  scale_fill_manual(values=c("royalblue", "orange"),name="", labels=c("Normal", "Seal 6018"))+
  ggthemes::theme_few()+
  xlim(1,90)+
  ylim(0,3000)+
  ylab("Jaw Motions/Day")+
  xlab("Day of Trip")+
  theme(panel.grid.major = element_line(size=0.3,colour="grey", linetype = "dashed"),
                legend.position = "none")
gg1
```


```{r KamiDepth~Trip, echo=FALSE,warning=FALSE, message = FALSE}

gg2<-ggplot(data=subset(dat_PB, group!="Benthic"),aes(x=dayID, y=KamiDepth))+
  geom_smooth(aes(fill=group, color=group), method="loess")+
  geom_point(data=subset(dat_PB, group=="Sick"), aes(color=group), size=1.5)+
  scale_color_manual(values=c("royalblue","orange"), name="", labels=c("Normal", "Seal 6018"))+
  scale_fill_manual(values=c("royalblue", "orange"),name="", labels=c("Normal", "Seal 6018"))+
  ggthemes::theme_few()+
  xlim(1,90)+
  ylim(600,100)+
  ylab("Depth (m)")+
  xlab("Day of Trip")+
  theme(panel.grid.major = element_line(size=0.3,colour="grey", linetype = "dashed"),
                legend.position = "none")
gg2

```



```{r Kami~ForagingTime, echo=FALSE,warning=FALSE, message = FALSE}

gg3<-ggplot(data=subset(dat_PB, group!="Benthic"),aes(x=ForDiveDurationSum/60/60/24, y=KamiNoSumPerDay))+
  stat_density_2d(aes(fill=group, alpha=..level..), geom="polygon", color="transparent")+
  scale_color_manual(values=c("royalblue","orange"), name="", labels=c("Normal", "Seal 6018"))+
  scale_fill_manual(values=c("royalblue", "orange"),name="", labels=c("Normal", "Seal 6018"))+
  ggthemes::theme_few()+
  ylab("Jaw Motions/Day")+
  xlab("%Time Foraging")+
  theme(panel.grid.major = element_line(size=0.3,colour="grey", linetype = "dashed"),
        legend.position = "none")+
  scale_x_continuous(label=scales::percent_format(accuracy=1))
gg3

```


```{r Density of Kami Depths, echo=FALSE,warning=FALSE, message = FALSE}

#NOTE THAT THIS MAY TAKE SOME TIME TO CREATE DENSITY DUE TO MANY DATA POINTS 
gg4<-ggplot(data=subset(z2_PB, group!="Benthic"),aes(y=KamiDepth))+
  geom_density(aes(fill=group, color=group), orientation="y", alpha=0.5 ,size=1)+
  scale_color_manual(values=c("royalblue","orange"), name="", labels=c("Normal", "Seal 6018"))+
  scale_fill_manual(values=c("royalblue", "orange"),name="", labels=c("Normal", "Seal 6018"))+
  ggthemes::theme_few()+
  ylab("Depth (m)")+
  xlab("Jaw Motion Density")+
  ylim(1500,0)+
  theme(panel.grid.major = element_line(size=0.3,colour="grey", linetype = "dashed"))+
  scale_x_continuous(expand=c(0,0),lim=c(0,0.0032))

#extract and save legend from gg4
legend<-cowplot::get_legend(gg4)

#remove legend from plot
gg4<-gg4+theme(legend.position="none")
  
```


```{r Figure 7 - Combined Plot, echo=FALSE}

gg5<-cowplot::plot_grid(gg1,gg2,gg3,gg4, labels="AUTO")

gg6<-cowplot::plot_grid(gg5, legend, rel_widths=c(1,0.2), nrow=1)
gg6

cairo_ps(filename = "Kami_Combined.eps",
         width = 10, height = 5, pointsize = 2,
         fallback_resolution = 500)
print(gg6)
dev.off()

```

